Market Expectations and Mangerial Turnover

### 2024-02-23 paper.qmd
sdfdsf

```{r}
#| include: false
rm(list = ls())
library(brms)
library(tidyverse)
library(rstan)
library (tidybayes)

@@

>>>>

```{r}
#| include: false
rm(list = ls())
library(brms)
library(tidyverse)
library(rstan)
library (tidybayes)
reticulate::use_condaenv("pymc")

@@

## Manager spell profiles
We build a hand-craft database on the complete manager turnover profiles of all professional football managers across 11 European leagues for 23 playing seasons up to 2023-2024.  We use 
three sources 1. [league of managers association](https://leaguemanagers.com) a body representing professional managers in English football. 2. [Soccer base](https://www.soccerbase.com) a betting website 3. [Transfermkt website](https://www.transfermarkt.co.uk) a large website which records manager, player and team profiles as well as a large array of analytics of the valuation of playing staff.  The raw data is gathered using a series of web scrapping algorithms. Our primary source of informatoin is Transfermkt, but we use other sources to validate these manager spells.

```{python}
import pandas as pd
from pandas_profiling import ProfileReport

spells_raw = pd.read_csv("raw_data/club_manager_histories_df.csv")

# Generating a report
profile = ProfileReport(spells_raw, title="Profile data", explorative=True)

# To display the report within a Jupyter Notebook
profile.to_notebook_iframe()
```
